Formatting Instructions for ICLR 2025 \\ Conference Submissions

### 2024-08-19 ICLR25/Paper_noProof.tex
Add paper in new format

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
\pagestyle{plain}

@@

\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vy}{\boldsymbol{y}}
\newcommand{\vW}{\boldsymbol{W}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vb}{\boldsymbol{bias}}
\newcommand{\val}{{\textrm{value}}}
\newcommand{\Val}{{\textrm{value}}}
\newcommand{\MILP}{{\textrm{MILP}}}
\newcommand{\LP}{{\textrm{LP}}}

@@

%\usepackage{amsmath, amsthm, amssymb, amsfonts}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{corollary}{Corollary}
%\theoremstyle{definition}
%\newtheorem{definition}{Definition}

@@

\title{I Compensate, therefore I Am \\ (accurate for DNN verification)}
\date{}

%\author{Yuke Liao}{CNRS@CREATE, Singapore}{yuke.liao@cnrsatcreate.sg}{}{}

%\author{Blaise Genest}{IPAL Lab, CNRS and CNRS@CREATE, France and Singapore}{blaise.genest@cnrsatcreate.sg}{}{}

%\author{Kuldeep Meel}{University of Toronto, Canada}{ meel@cs.toronto.edu}{}{}

%\author{Shaan Aryaman}{NYU Courant Institute of Mathematical Sciences, United States}{aryaman.shaan@gmail.com}{}{}

%\author{John Q. Public}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}
%\authorrunning{Y. Liao, B. Genest, K. Meel and S. Aryaman} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

%\Copyright{Liao Yuke, Blaise Genest, Kuldeep Meel and Shaan Aryaman} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[100]{} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\begin{document}

@@

	\begin{abstract}

		Deep Neural Networks (DNNs) verification has evolved into a robust field of research, furnished with a plethora of methodologies and tools designed for formal correctness verification. This area even boasts an annual competition to benchmark these tools. Formally, the question it addresses is whether a given DNN upholds a specified property across a set of input data. For instance, it can ascertain local robustness around an input $\vx$ by verifying if the i-th output neuron consistently demonstrates the highest weight amongst all output neurons within a certain vicinity of $\vx$. In recent years, the focus has shifted towards integrating various efficient techniques—such as branch and bound, multi-neuron encoding, and MILP encoding—to optimize the balance between speed and accuracy. Although modern verifiers can efficiently validate relatively large DNNs (with tens of thousands of neurons), the challenge persists, especially when dealing with certain DNNs, even smaller ReLU DNNs comprising hundreds of neurons, thereby highlighting the ongoing need for innovative methodologies.

		In this paper, we analyse efficient algorithms  for verifying ReLU DNNs, examining abstractions like DeepPoly, Linear Programming, PRIMA, and various versions of Crown. We identify the primary cause of accuracy loss: {\em compensations}. Compensations occur when dual paths exist between a neuron pair, with one path carrying positive weights and the other negative, leading to a partial offset. However, accurately quantifying this offset is complex due to the ReLU activation functions. Leveraging this insight, we introduce a novel approach for achieving promising speed-accuracy trade-offs. This involves conducting numerous queries with a limited number of 'open' ReLU nodes (considering both linear modes) rather than the traditional approach of fewer queries with potentially many 'open' ReLU nodes. These findings not only present practical implications but also pave the way for various applications of the concept of compensating paths in the realm of DNN verification.

	\end{abstract}

@@

	\input{introduction}

	\input{relatedwork}

@@

	In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
	capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in \cite{prima,crown}.
	To simplify the notations, we restrict the presentation to feed-forward, 
	fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
	$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.

@@

\bibliographystyle{plain}
\bibliography{references}

@@

\section{Ranking of Compensating Pairs}

In this subsection, we will introduce the method to choose open nodes for MILP model based on compensating pairs.

Based on No Diamond Theorem, for a target node, in its MILP model, if we open all nodes in compensating pairs, then we can get the exact values of upper and lower bound of the target node. However, in practice, this is still too expensive because we will still need to open too many nodes. So we can only choose a limited number of compensating pairs and nodes. This is by setting a parameter $O$ such that the process only choose at most $O$ many nodes to open. Therefore, in this subsection, we will introduce the process of open node chosen: given a target node, choose up to $O$ many nodes to open.

Basically, we do the process of open nodes chosen for one target node each time, that is, receive one target node (and other data) as input each time. But in principle, we can develop a method receive more than one nodes as input. But in our experiences, this does not work well.

This process is not the unique method but the most natural way to choose open nodes. We introduce it in three steps from the simplest case to more complex case.

\subsubsection*{Value of a pair}

For a compensating pair, if $V_1,V_2$ are the values of two paths, then the value of this compensating pair is defined by: $V=\min(|V_1|,|V_2|)$.

\subsection*{Case: Source node fixed}

The simplest case is when we only consider compensating pairs with a fixed source node.

In this case, the process is very simple: enumerate all compensating pairs, and then sort them by their values. Finally, from the first to the last compensating pair, pick all unstable nodes in its two paths except the target and source nodes into the list of open nodes, until $O$ many open nodes.

%\subsubsection*{Sort all paths by values}
%
%The first step is to sort all paths by their values and divide paths into two groups, a group of paths with positive values and a group of paths with negative values.
%
%Since we have set a bound $O$ for open nodes, we will store  a fixed number of path for each group.
%
%\subsubsection*{Sort pairs by values}
%
%The second step is to sort all pairs by their values. Enumerate paths from the positive group and the negative group one by one and put the pairs obtained into a new list of pairs. Then sort all pair by their values from largest to the smallest: recall that the value of a pair $\langle P_1,P_2\rangle$ is $\min(|V_1|,|V_2|)$.
%
%\subsubsection*{Choosing nodes}
%
%The third step is to choose nodes from the list of pairs. According to the sorted list of pairs, enumerate pair one by one; for each pair, pick the nodes unstable in the two paths except the source and target node into the open node list. Repeat this process until $O$ nodes chosen or reach the end of the list.
%
%\subsubsection*{Pseudocode}
%
%The following needs a chart of pseudo-code
%
%\vspace*{1ex}
%
%1. Enumerate all path from the fixed source node to the target node. 
%
%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
%
%3. Divide all paths into two group: positive paths and negative paths.
%
%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
%
%5. For each pair, its value is the min of the weight positive paths and absolute negative values.
%
%6. From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node. 
%
%7. Repeat 6 until choosing sufficiently many nodes.
%

\subsection*{Case: Source nodes in one layer}

The more general case is when the source node can be any node in a fixed layer. In this case, the process is very similar to previous case, except the value of a pair.

In this case, for a pair $P_1,P_2$ with values $V_1,V_2$ with the source node $a$, its value is $\min(|V_1|,|V_2|)\times \text{upper bound of } a$.

%\subsubsection*{Pseudocode}
%
%The following needs a chart of pseudo-code
%
%\vspace*{1ex}
%
%1. Enumerate all path from the fixed source node to the target node. 
%
%2. For each path, compute its weight, that is the products of all $W_{aa'}$ along the path.
%
%3. Divide all paths into two group: positive paths and negative paths.
%
%4. Pair positive paths and negative paths from those with larger absolute values to smaller. 
%
%5. For each pair, its value is the min of the weight positive paths and absolute negative values, times the upper bound (at least 0) of the source node.
%
%6. From pairs with larger values to smaller, pick path one by one, and check all intermediate nodes (nodes except source and target) of each path, and if any of them is unstable ($u>0$ and $l<0$), then open this node. 
%
%7. Repeat 6 until choosing sufficiently many nodes.

\subsection*{Case: Source nodes in different layers}

The general case is that when the location of source nodes can be in different layers. This case is much more complex, because the scale level of values of paths from different layers are very different: usually a weight will be very small since every layer has a large number of nodes, therefore values of longer paths are products of more small numbers, and is definitely much smaller. If we sort all compensating pairs from different layers directly, then a very long initial segment of this list will be occupied by compensating pairs with the shortest length. Therefore, we need use some scale factors when comparing values of compensating pairs of different length.

In our experiments, we only consider the paths of length 3 (the source node is 2 layers before) and length 4 (the source node is 3 layers before). We will dynamically adjust the values during the process of node chosen. In text, the process of node chosen for length 3 plus length 4 is as follows:

\vspace*{1ex}

1. Generate the two lists of pairs sorted by their values for source nodes in 2 layers before the target node and 3 layers before separately as in the previous case.

2. Enumerate pair from two lists one by one by their values and pick nodes as previous case. When comparing the values between pairs of length 4 and pairs of length 3, multiply the numbers of nodes in 1 layer before to the value of pair of length 4.

In formula, when the target node is in layer $L$, for a pair $P_3$ of length 3 with value $V_3$ and a pair $P_4$ of length 4 with value $V_4$, if we have chosen $N$ nodes in layer $L-1$. Then the adjusted values for $P_3$ and $P_4$ are: $$V_3, N\cdot V_4.$$ Then we pick the next pair by the adjust value in two lists.

3. Repeat 2 until choosing sufficiently many nodes.

\vspace*{1ex}

The pseudo-code is as follows ():

\begin{algorithm}
\caption{Process for length 3 + length 4}
\KwData{Sorted lists of length 3 + length 4}
\KwResult{Open node list}

Let $N = 0$ be the number of Chosen length 4 pair.

\While{len(Open node) $<O$}{
	Pick the first element $P_3$ in the list of length 3\;

	Let $V_3$ be the value of $P_3$\;

	Pick the first element $P_4$ in the list of length 4\;

	Let $V_4$ be the value of $P_4$\;

	\If{$V_3 > V_4 \cdot N$}{
		Add nodes in $P_3$ into Open list\;
		Number of Chosen lentgh pair $N$ += 1\; 
	}
	\Else{
		Add nodes in $P_4$ into Open list\;
	}
}
\end{algorithm}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{iclr2025_conference,times}
% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\pagestyle{plain}

@@

\newcommand{\vW}{\boldsymbol{W}}

\newcommand{\val}{{\textrm{value}}}
\newcommand{\Val}{{\textrm{value}}}
\newcommand{\MILP}{{\textrm{MILP}}}
\newcommand{\LP}{{\textrm{LP}}}

@@

\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}

@@

\title{Formatting Instructions for ICLR 2025 \\ Conference Submissions}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

@@

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

@@

\input{introduction}
%
\input{relatedwork}

@@

In this paper, we will use lower case latin $a$ for scalars, bold $\boldsymbol{z}$ for vectors, 
capitalized bold $\boldsymbol{W}$ for matrices, similar to notations in.
To simplify the notations, we restrict the presentation to feed-forward, 
fully connected ReLU Deep Neural Networks (DNN for short), where the ReLU function is $ReLU : \mathbb{R} \rightarrow \mathbb{R}$ with
$ReLU(x)=x$ for $x \geq 0$ and $ReLU(x)=0$ for $x \leq 0$, which we extend componentwise on vectors.

@@

\bibliography{references}
\bibliographystyle{iclr2025_conference}

@@

### 2024-08-19 ICLR25/comppaths.tex
Add paper in new format

First, notice that by continuity of all the functions used in the DNNs, it suffices to show both theorem for $\gamma=\alpha$ and $\gamma=\beta$.
%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
Consider a target neuron $z$.
In case there is no compensating path, we can assign an "influence sign" $S(n)$ to each neuron $n$: $S(n)=0$ if all paths from $n$ to $z$ has weight 0, $S(n)=+1$ if all paths have positive weights, and $S(n)=-1$ if they have negative weights. E.g., $S(n)=-1$ means that $\val_{\vx}(z)$ will increase if $\val_{\vx}(n)$ decreases. 
Specifically, $S(n)$ is {\em not} the sign of $\val_{\vx}(n)$, and biases have no impact on  $S(n)$: bias in $n$ changes $\val_{\vx}(n)$, not $S(n)$, while biases in between $n$ and $z$ will not change the influence of $\val_{\vx}(n)$ over $\val_{\vx}(z)$ (though it will change $\val_{\vx}(z)$ itself). We introduce $\vx^{*}, \vx^{\sharp}$:
%Using the concept of sign,

@@

Hence $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
for $[\alpha, \beta]$ computed by the Box abstraction. We conclude Theorem \ref{th1} by invocking continuity. The full proof is in appendix A.

@@

\begin{proposition}
For a node $b$ with $S(b)=1$ and $b'$ with $S(b())=-1$:

@@

Theorem \ref{th2} theoretically computes accurate bounds by iteratively applying MILP$_{X}$ to each node, layer by layer. Practically, however, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$. Instead, an interesting trade off between speed and accuracy is to set a threshold on the strength of compensation. Paths falling below this threshold are deemed to not warrant an individual integer variable due to insufficient compensatory strength. We denote the resultant subset of nodes situated on paths with substantial compensation as $Z_n$. In practical applications, one might consider selecting the $K$ nodes that are involved in the most significant compensating paths to construct the set $Z_n$, with $K$ being a relatively small integer. This strategy effectively provides a trade-off between the algorithm's performance and the precision of the results. The pseudo-code for \CMP is presented in Algorithm \ref{algo1}.

@@

CMP($K$) has a worst case complexity bounded by $O(N \MILP(N,K))$, 
where $N$ is the number of nodes of the DNN, 
and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound. Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$. 
%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
CMP uses 20 threads.

>>>>

First, notice that by continuity of all the functions used in the DNNs, it suffices to show both theorem for $\gamma=\alpha$ and $\gamma=\beta$.
%Intuitively, our first proof shows that if there are no compensation, then there are no correlations between nodes.
Consider a target neuron $z$.
In case there is no compensating path, we can assign an "influence sign" $S(n)$ to each neuron $n$: $S(n)=0$ if all paths from $n$ to $z$ has weight 0, $S(n)=+1$ if all paths have positive weights, and $S(n)=-1$ if they have negative weights. E.g., $S(n)=-1$ means that $\val_{\vx}(z)$ will deacrese if $\val_{\vx}(n)$ increases. 
Specifically, $S(n)$ is {\em not} the sign of $\val_{\vx}(n)$, and biases have no impact on  $S(n)$: bias in $n$ changes $\val_{\vx}(n)$, not $S(n)$, while biases in between $n$ and $z$ will not change the influence of $\val_{\vx}(n)$ over $\val_{\vx}(z)$ (though it will change $\val_{\vx}(z)$ itself). We introduce $\vx^{*}, \vx^{\sharp}$:
%Using the concept of sign,

@@

We can then prove that $\val_{\vx^\star}(z)=\beta$ and $\val_{\vx^\sharp}(z)=\alpha$,
for $[\alpha, \beta]$ computed by the Box abstraction. 
We conclude Theorem \ref{th1} by continuity. The full proof is in appendix A.

@@

\begin{proposition}
For a node $b$ with $S(b)=1$ and $b'$ with $S(b)=-1$:

@@

Theorem \ref{th2} theoretically computes accurate bounds by iteratively applying MILP$_{X_n}$ to each node $n$, layer by layer. Practically, however, the set $X_n$ includes a substantial portion of the nodes from all preceding layers up to layer $k-1$ for a given node $n$ in layer $k$. Instead, an interesting trade off between speed and accuracy is to set a threshold on the strength of compensation. Paths falling below this threshold are deemed to not warrant an individual integer variable due to insufficient compensatory strength. We denote the resultant subset of nodes situated on paths with substantial compensation as $Z_n$. In practical applications, one might consider selecting the $K$ nodes that are involved in the most significant compensating paths to construct the set $Z_n$, with $K$ being a relatively small integer. This strategy effectively provides a trade-off between the algorithm's performance and the precision of the results. The pseudo-code for \CMP is presented in Algorithm \ref{algo1}.

@@

CMP($K$) has a worst case complexity bounded by $O(N \cdot \MILP(N,K))$, 
where $N$ is the number of nodes of the DNN, 
and $\MILP(N,K)$ is the complexity of solving a MILP program with $K$ integer variables and $N$ linear variables.
We have $\MILP(N,K) \leq 2^K \LP(N)$ where $\LP(N)$ is the Polynomial time to solve a Linear Program with $N$ variables, $2^K$ being an upper bound. Solvers like Gurobi are quite adept and usually do not need to evaluate all $2^K$ ReLU configurations to deduce the bounds.
It is worth mentioning that the "for" loop iterating over neurons $n$ in layer $k$ (line 2) can be executed in parallel, because the computation only depends on bounds from preceding layers, not the current layer $k$. 
%This parallelization results in a time complexity of $O(\sum_{i=1}^{\ell} \MILP(N_{i-1},K))$, where $\ell$ denotes the total number of layers and $N_i$ the count of neurons in layers $0, ..., i$. 
CMP uses 20 threads.

### 2024-08-19 ICLR25/introduction.tex
Add paper in new format

%As a starting point, we sought to understand properties of DNNs that make them hard to verify.
Our key finding is a new notion of {\em compensations}, that explains why bounds are inaccurate. Formally, a {\em compensating pair of paths} $(\pi,\pi')$ between neurons $a$ and $b)$ is such that $w < 0 < w'$ for $w,w'$ the products of weights seen along $\pi$ and $\pi'$ respectively. Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with 
$(w+w') weight(a)$ by $\pi$ and $\pi'$. As $w,w'$ have opposite signs, they will compensate (partly) each other. The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$. However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which the efficient tools try to avoid because it is very time-consuming (combinatioral explosion as the problem is NP-hard \cite{Reluplex}).
%; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust. 
Our three main contributions address the challenges of inaccuracies when verifying DNNs:
\begin{enumerate}
	\item  Our first main contribution establishes, through Theorem \ref{th1}, the foundational understanding that the compensating pairs are the 	%primary 
	source of {\em all} inaccuracies, 
	 as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate. This is confirmed experimentally by the fact that 
	 DNNs easier to verified have less compensation strenght than verification agnostic DNNs. 
	This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs. Nonetheless, this insight lays the groundwork for our innovative approach, {\em relaxing} the usual but inefficient Mixed Integer Linear Program (MILP) formulation encoding exactly DNNs \cite{MILP}. To compute bounds for $z$, we encode as binary variables only ReLU nodes on {\em compensating paths with target $z$}; other nodes, in particular those on compensating paths to neurons before $z$ are encoded using the much faster linear relaxation. To take into account indirectly the compensating paths to previous nodes, we inductively compute bounds for every neuron layer by layer, and use these bounds of previous neurons in the MILP encoding for $z$. This is more efficient, as the number of binary nodes is strongly reduced. However, the question remains how accurate is it?

>>>>

%As a starting point, we sought to understand properties of DNNs that make them hard to verify.
Our key finding is a new notion of {\em compensations}, that explains why bounds are inaccurate. Formally, a {\em compensating pair of paths} $(\pi,\pi')$ between neurons $a$ and $b)$ is such that $w < 0 < w'$ for $w,w'$ the products of weights seen along $\pi$ and $\pi'$ respectively. Ignoring the (ReLU) activation functions, the weight of $b$ is loaded with 
$(w+w') weight(a)$ by $\pi$ and $\pi'$. As $w,w'$ have opposite signs, they will compensate (partly) each other. The compensation is only partial due to the ReLU activation seen along the way of $\pi$ which can "clip" a part of $w \cdot weight(a)$, and similarly for $\pi'$. However, it is very hard to evaluate by how much without explicitly considering both phases of the ReLUs, which the efficient tools try to avoid because it is very time-consuming (combinatorial explosion as the problem is NP-hard \cite{Reluplex}).
%; for instance, what is a differentiating  feature between DNNs trained in natural way (i.e., without explicit concern for robustness) versus the DNNs trained to be robust. 
Our three main contributions address the challenges of inaccuracies when verifying DNNs:
\begin{enumerate}
	\item  Our first main contribution establishes, through Theorem \ref{th1}, the foundational understanding that the compensating pairs are the 	%primary 
	source of {\em all} inaccuracies, 
	 as in their absence, even the simplest Box abstraction (and most abstractions under consideration) is fully accurate. This is confirmed experimentally by the fact that 
	 DNNs easier to verified have less compensation strength than verification agnostic DNNs. 
	This revelation, while theoretically pivotal, has limited practical applicability as most networks inherently possess compensating pairs. Nonetheless, this insight lays the groundwork for our innovative approach, {\em relaxing} the usual but inefficient Mixed Integer Linear Program (MILP) formulation encoding exactly DNNs \cite{MILP}. To compute bounds for $z$, we encode as binary variables only ReLU nodes on {\em compensating paths with target $z$}; other nodes, in particular those on compensating paths to neurons before $z$ are encoded using the much faster linear relaxation. To take into account indirectly the compensating paths to previous nodes, we inductively compute bounds for every neuron layer by layer, and use these bounds of previous neurons in the MILP encoding for $z$. This is more efficient, as the number of binary nodes is strongly reduced. However, the question remains how accurate is it?
